---
title: "Lab 00 - Hello IDS!"
author: "LINCOLN LUK"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Sean King", "Kitty Ruan", 
           "Will Cornes", "Louis Hursthouse"),
  github_username = c("mcgregors-garden", "zestking", "kitten", 
                      "corny", "hursty"), 
  colour = c("powderblue", "brown", "red", 
             "grey", "darkblue"),
  hobby = c("Hopping", "Singing", "Dancing", 
            "Shooting", "Cricket"),
  favourite_number = c(2, 6, 7, 4, 1)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

Plots favourite number to each username and colourcoded by their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number",
          title = "Lab 00")
```

Allows you to modify the axis labels, and titles

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

If more people were included into the plot, the plot would look flat as not many people will have the same hobbies so the plot would look flat and small. 
Maybe a pie chart would present the data better.